\cvsection{Teaching}

\cvevent{Volunteer Instructor}{\href{https://www.saturdaykids.com/social-mission/code-in-the-community/}{Code in the Community}}{August 2019 -- Ongoing}{}
Code in the Community is a program that provides free coding lessons to children of disadvantaged families in Singapore. As instructor, my role is to prepare educational presentations, explain programming concepts to the class, lead the students through hands-on assignments, and provide students with one-on-one help to supplement the efforts of the assistants.

\divider

\cvevent{Volunteer Assistant}{\href{https://www.saturdaykids.com/social-mission/code-in-the-community/}{Code in the Community}}{May 2019 -- July 2019}{}
As assistant, my role was to help keep the students focused and organized, as well as provide students with one-on-one guidance as they worked through the hands-on assignments.

\divider

\cvevent{Teaching Assistant}{Georgia Institute of Technology}{August 2013 -- May 2014}{}
CS 8803: Humanoid Robotics. Multidisciplinary project-oriented class which introduced students to the fundamentals of planning, control, and operation for humanoid robot platforms. In addition to providing technical assistance to the students, I taught a series of voluntary ``crash courses'' for students who lacked some of the necessary technical background for the class.

\divider

\cvevent{Aerospace Department Tutor}{University of Illinois at Urbana-Champaign}{August 2010 -- May 2011}{}
Assisted fellow aerospace undergraduates with technical courses, both fundamental and domain-specific. This position was sponsored by the Aerospace Department at the University of Illinois.